\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-23 paper/paper 2/dc-2015.tex
DC 2015

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

@@

% footnotes
\usepackage{scrextend}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

@@

%\usepackage{listings}% http://ctan.org/pkg/listings
%\lstset{
  %numbers=left,numbersep=2mm,frame=single,mathescape,fontsize=\scriptsize
%}

@@

\newenvironment{gcotable-1}{
  \scriptsize
  \sffamily
  \vspace{0cm}
  \begin{tabular}{l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
}

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
	\end{center}
}

\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
	\end{center}
}

\newenvironment{evaluation-generic-overview}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\begin{center}
  \begin{tabular}{l|c|c}
  \hline
  \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
  \hline

}{
  \hline
  \end{tabular}
  %\linebreak
	\end{center}
}

@@

% pipe
%\usepackage[T1]{fontenc}

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

\setcounter{secnumdepth}{5}

@@

%
%
%\title{Formulating RDF Constraints and \\ Validating RDF Data Generically}
\title{Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box }
%\subtitle{}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and Kai Eckert\inst{3}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS - Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{erman@informatik.uni-mannheim.de} 
\and
Stuttgart Media University, Germany \\
\email{eckert@hdm-stuttgart.de} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}

More and more domains adopt Linked Data principles
and seek for ways to ensure data quality by validating RDF data according to predefined constraints.  In particular, as many communities are used to have this functionality in the XML world.
XML Schema is the standard language to formulate constraints to validate XML documents.
For RDF, however, there are several languages which can be used to express constraints on RDF data - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text. In abstract and introduction, we just give general idea so at such points we better focus on flow.  
We identified requirements to formulate constraints for  validating RDF data and mapped each requirement to a constraint type.
The majority of these constraint types can be expressed in description logics which provides their logical underpinning.

%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
%%(whether expressible in description logics or not).
%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.

@@

\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Linked Data, Semantic Web}
\end{abstract}
%

% ---------------

@@

In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
Bosch et al. identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.

@@

\section{Motivation}

@@

With \emph{minimum qualified cardinality restrictions} (\emph{R-75/81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}}, but also specifically (\emph{specific constraint}) by multiple constraint languages:

@@

We provide a validation environment\footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@

\subsection{RDF Validation Semantics}

@@

We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which
we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We express constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

@@

\tb{Frage an Kai: wann soll ich in kursiv hervorheben?}

@@

\subsection{Basic Terminology for the Formulation of RDF Constraints}

@@

As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.

@@

Constraints can be expressed either generically (\emph{generic constraints}) by the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages.
As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
The majority of the constraint types can be expressed in \emph{DL}.
In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}). 
%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary. "in different contexts they call it signature which is the same thing". Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
\er{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}

\subsection{\emph{Simple Constraints} (Expressible in \emph{DL})}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Publication & author & - & Person & $\geq$ & 1 \\
		\end{tabular}
	\caption{Property Constraint - Cardinality Restriction}
	\label{tab:property-constraint-cardinality-restriction}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
		\end{tabular}
	\caption{Property Constraint - Object Property Paths}
	\label{tab:property-constraint-object-property-paths}
\end{table}

\subsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Book & identifier & - & ISBN & $\forall$ & - \\
      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
		\end{tabular}
	\caption{Simple Constraint (Not Expressible in DL)}
	\label{tab:simple-constraint-not-expressible-in-dl)}
\end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
The \emph{literal pattern matching} constraint type introduces the new \emph{constraining element} \emph{regex},
for which a validation mechanism has to be implemented.
Validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}.

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
class & $\neg$E & - & - & E & $\neg$ & - \\
class & E & - & - & A, B & $\sqcap$ & - \\
class & $\neg$F & - & - & F & $\neg$ & - \\
class & F & - & - & C, D & $\sqcap$ & - \\
class & A & - & - & A1, A2 & $\sqcap$ & - \\
property & A1 & isbn & - & string & $\geq$ & 1 \\
property & A2 & isbn & - & string & $\leq$ & 1 \\
class & B & - & - & B1, B2 & $\sqcap$ & - \\
property & B1 & title & - & string & $\geq$ & 1 \\
property & B2 & title & - & string & $\leq$ & 1 \\
class & C & - & - & C1, C2 & $\sqcap$ & - \\
property & C1 & issn & - & string & $\geq$ & 1 \\
property & C2 & issn & - & string & $\leq$ & 1 \\
class & D & - & - & D1, D2 & $\sqcap$ & - \\
property & D1 & title & - & string & $\geq$ & 1 \\
property & D2 & title & - & string & $\leq$ & 1 \\
		\end{tabular}
	\caption{Complex Constraints}
	\label{tab:complex-constraints}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & E, F & XOR \\
class & E & - & - & A, B & $\sqcap$ \\
class & F & - & - & C, D & $\sqcap$ \\
property & A & isbn & - & string & = & 1 \\
property & B & title & - & string & = & 1 \\
property & C & issn & - & string & = & 1 \\
property & D & title & - & string & = & 1 \\
		\end{tabular}
	\caption{Simplified Complex Constraints}
	\label{tab:simplified-complex-constraints}
\end{table}

\subsection{\emph{Complex Constraints} as \emph{Simple Constraints}}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		\end{tabular}
	\caption{Irreflexive Object Properties as Complex Constraints}
	\label{tab:irreflexive-object-properties-as-complex-constraints}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & $\top$ & authorOf & - & - & irreflexive & - \\
		\end{tabular}
	\caption{Irreflexive Object Properties as Simple Constraints}
	\label{tab:irreflexive-object-properties-as-simple-constraints}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse & - \\
property & Book & isbn$^{-}$ & - & - & functional & - \\
		\end{tabular}
	\caption{Primary Key Properties as Complex Constraints}
	\label{tab:primary-key-properties-as-complex-constraints}
\end{table}

@@

%\section{Transformations and Automatic Validation of Specific Constraints}
%\section{Transformations between Specific Constraints (Expressed by Different Constraint Languages)}
%\section{Transformations between Specific Constraints}
\section{How to Improve the Understandability of Constraints}
\label{sec:transformations}

@@

\tb{0.75 page / explain how typical constraints are expressed by different constraint languages}

@@

>>>>

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass[a4paper,fontsize=11pt]{scrartcl}

% Anpassungen an DC Template
\usepackage[a4paper, left=2.9cm,right=2.87cm,bottom=3cm,top=3cm,headsep=1.27cm]{geometry}
\setlength{\parskip}{0.5em}
\renewcommand{\tablename}{TABLE} 
\renewcommand{\figurename}{FIG} 
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 2pt minus 2pt}{6pt plus 1pt minus 1pt}
\titlespacing\subsection{0pt}{12pt plus 2pt minus 2pt}{3pt plus 1pt minus 1pt}
\addtokomafont{title}{\fontsize{14pt}{1em}\selectfont}
\setkomafont{section}{\fontsize{12pt}{0pt}\selectfont}
\addtokomafont{subsection}{\fontsize{11pt}{0pt}\selectfont}
\addtokomafont{author}{\fontsize{12pt}{1em}\selectfont}
\usepackage{scrpage2}
\clearscrheadfoot
\pagestyle{scrheadings}
\renewcommand*{\titlepagestyle}{scrheadings}
\chead{\fontsize{11pt}{0pt}\selectfont Proc. Int'l Conf. on Dublin Core and Metadata Applications 2015}
\usepackage{apacite}

\date{}

@@

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

% \usepackage{makeidx}  % allows for indexgeneration -- yes, but we don't need this

\usepackage{amsmath}

@@

@@

@@

@@

\title{\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box}

\author{Thomas Bosch\\GESIS – Leibniz Institute \\for the Social Sciences, Germany\\thomas.bosch@gesis.org \and Kai Eckert\\Stuttgart Media University, Germany\\eckert@hdm-stuttgart.de}

\maketitle
\vspace{-3em}
\section*{Abstract}
Increasingly, various domains adopt Linked Data principles
and seek for ways to ensure data quality by validating RDF data according to predefined constraints,
in particular, as many communities are used to have this functionality in the XML world.
%XML Schema is the standard language to formulate constraints to validate XML documents.
%For RDF, however, there are several constraint languages - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
To formulate constraints and to validate RDF data, several languages exist or are currently developed,
but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners
% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text. In abstract and introduction, we just give general idea so at such points we better focus on flow.  
Based on our work in the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}, 
we published by today 81 types of constraints that are required by various stakeholders for data applications.
%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
%%(whether expressible in description logics or not).
%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.

@@

\hspace{-1.4em}
\textbf{Keywords:}
RDF validation; RDF constraints; RDF validation requirements; Linked Data; Semantic Web

@@

In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where experts from industry, government, and academia discussed first use cases for RDF constraint
%\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} 
formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
which is available for contribution.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
We identified 81 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.

@@

\subsection{Motivation and Overview}

@@

Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
\emph{Minimum qualified cardinality restrictions} (\emph{R-75}), e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}. 
With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may restrict
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}}, but also specifically (\emph{specific constraint}) by multiple constraint languages:

@@

We provide a validation environment\footnote{Online available at \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@

\subsection{Underlying Semantics}

@@

We recently published a technical report \cite{BoschNolleAcarEckert2015} (serving as appendix of this paper) in which
we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We express constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

@@

@@

\subsection{Basic Terminology}
%\subsection{Basic Terminology for the Formulation of RDF Constraints}

@@

As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.

@@

Constraints can be expressed either generically (\emph{generic constraints}) by the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages.
As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
The majority of the constraint types can be expressed in \emph{DL}.
In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}). 
%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary. "in different contexts they call it signature which is the same thing". Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}

\subsection{\emph{Simple Constraints}}

\subsubsection{\emph{Simple Constraints} (Expressible in \emph{DL})}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Property Constraint - Cardinality Restriction}
	\label{tab:property-constraint-cardinality-restriction}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Publication & author & - & Person & $\geq$ & 1 \\
		\end{tabular}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Property Constraint - Object Property Paths}
	\label{tab:property-constraint-object-property-paths}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
		\end{tabular}
\end{table}

\subsubsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Simple Constraint (Not Expressible in DL)}
	\label{tab:simple-constraint-not-expressible-in-dl)}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Book & identifier & - & ISBN & $\forall$ & - \\
      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
		\end{tabular}
\end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
The \emph{literal pattern matching} constraint type introduces the new \emph{constraining element} \emph{regex},
for which a validation mechanism has to be implemented.
Validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}.

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Complex Constraints}
	\label{tab:complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
class & $\neg$E & - & - & E & $\neg$ & - \\
class & E & - & - & A, B & $\sqcap$ & - \\
class & $\neg$F & - & - & F & $\neg$ & - \\
class & F & - & - & C, D & $\sqcap$ & - \\
class & A & - & - & A1, A2 & $\sqcap$ & - \\
property & A1 & isbn & - & string & $\geq$ & 1 \\
property & A2 & isbn & - & string & $\leq$ & 1 \\
class & B & - & - & B1, B2 & $\sqcap$ & - \\
property & B1 & title & - & string & $\geq$ & 1 \\
property & B2 & title & - & string & $\leq$ & 1 \\
class & C & - & - & C1, C2 & $\sqcap$ & - \\
property & C1 & issn & - & string & $\geq$ & 1 \\
property & C2 & issn & - & string & $\leq$ & 1 \\
class & D & - & - & D1, D2 & $\sqcap$ & - \\
property & D1 & title & - & string & $\geq$ & 1 \\
property & D2 & title & - & string & $\leq$ & 1 \\
		\end{tabular}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Simplified Complex Constraints}
	\label{tab:simplified-complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & E, F & XOR \\
class & E & - & - & A, B & $\sqcap$ \\
class & F & - & - & C, D & $\sqcap$ \\
property & A & isbn & - & string & = & 1 \\
property & B & title & - & string & = & 1 \\
property & C & issn & - & string & = & 1 \\
property & D & title & - & string & = & 1 \\
		\end{tabular}
\end{table}

\subsubsection{\emph{Complex Constraints} as \emph{Simple Constraints}}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Irreflexive Object Properties as Complex Constraints}
	\label{tab:irreflexive-object-properties-as-complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
		\end{tabular}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Irreflexive Object Properties as Simple Constraints}
	\label{tab:irreflexive-object-properties-as-simple-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & $\top$ & authorOf & - & - & irreflexive & - \\
		\end{tabular}
\end{table}

@@

\begin{table}
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Primary Key Properties as Complex Constraints}
	\label{tab:primary-key-properties-as-complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse & - \\
property & Book & isbn$^{-}$ & - & - & functional & - \\
		\end{tabular}
\end{table}

@@

%\section{Transformations and Automatic Validation of Specific Constraints}
%\section{Transformations between Specific Constraints (Expressed by Different Constraint Languages)}
%\section{Transformations between Specific Constraints}

\section{How to Improve the Understandability of Constraints}
\label{sec:transformations}

@@

\tb{explain how typical constraints are expressed by the most common constraint languages}

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

@@

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----

-----
